Music Perception 2020: Stimuli profiles (random)

### 2020-10-12 material/stimuli/R/analysis/random.Rmd
filtered >> random
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# merge all data files into one
data <- data.table()
for (i in 1:length(lf_a_t)){
  data_i <- fread(file.path("../filtered/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_a_p)){
  data_i <- fread(file.path("../filtered/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_t)){
  data_i <- fread(file.path("../filtered/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_p)){
  data_i <- fread(file.path("../filtered/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}

>>>>

# merge all data files into one
data <- data.table()
for (i in 1:length(lf_a_t)){
  data_i <- fread(file.path("../random/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_a_p)){
  data_i <- fread(file.path("../random/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_t)){
  data_i <- fread(file.path("../random/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_p)){
  data_i <- fread(file.path("../random/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
